---
title: "Social Cost of Crashes by Region"
author: "Tieta Putri"
date: "10/05/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("crash_analysis.R")
```

## Minor, serious and fatal crash cost by region {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, results="asis"}

for (i in region$region){

  cat("### ", i, "\n")
  cat("\n")
  print(plots_crash[[i]])
  cat("\n")
  cat("\n")
}
cat("\n")

```


## Minor, serious and fatal crash percentage cost by region {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, results="asis"}

for (i in region$region){

  cat("### ", i, "\n")
  cat("\n")
  print(plots_crash_pct[[i]])
  cat("\n")
  cat("\n")
}
cat("\n")

```

## Fatal pedestrian crash cost by region {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, results="asis"}

for (i in region$region){

  cat("### ", i, "\n")
  cat("\n")
  print(plots[[i]])
  cat("\n")
  cat("\n")
}
cat("\n")

```


## Fatal pedestrian crash cost as a percentage of fatal crash cost by region {.tabset .tabset-fade .tabset-pills}

```{r, echo=FALSE, results="asis"}

for (i in region$region){

  cat("### ", i, "\n")
  cat("\n")
  print(plots_pedestrian_fatal[[i]])
  cat("\n")
  cat("\n")
}
cat("\n")

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
